### 2016-12-18 ms/ms.tex
small changes to mc

Species in ecological communities are linked through ecological
interactions. As the world continues to lose species at an alarming
rate \citep{dunn2009sixth, barnosky2011has}, anticipating a
community's ability to resist collapse will depend on the strength of
each interaction network and the species within it \citep{Memmott2004,
  Rezende2007, Bascompte2009, Thebault2010}. Furthermore, it has been
show that biodiversity has a pivotal role in maintaining ecosystems
services \citep{cardinale-2012-59}. Thus, to safeguard ecological
function, it has become increasingly imperative to aid the recovery of
lost interactions and component biodiversity and by facilitating the
assembly of robust interaction networks via ecological restoration
\citep{menz-2010-4}. However, we know very little about how ecological
networks assemble in general, rendering restoration of interacting
communities quite difficult.

Preferential attachment, the most widely explored mechanism of network
assembly, predicts that species entering a network are more likely to
interact with species that are already well-connected \citep[the
``rich-get-richer'' principle,][]{barabasi1999emergence}. In
pollination systems --- a particularly ubiquitous mutualism
\citep{ollerton-2011-321, klein-2007-303} --- some studies have found
support for this assembly mechanism. Investigating the day-to-day,
temporal assembly of a plant-pollinator network within a season,
\cite{Olesen2008} found that phenologically new plant and pollinator
species tended to interact with already well-connected species,
potentially because these species are either more abundant or
temporally persistent. Using a space-for-time substitution to study
primary succession, \cite{albrecht2010plant} also found evidence that
assembly along a glacier foreland occurred through preferential
attachment. Specifically, network nestedness (i.e, a core group of
generalists interacts with both specialist and generalist species)
increased as the community aged \citep{albrecht2010plant}. An increase
in nestedness could have occurred via the preferential attachment
process, whereby specialist species attach to the well-connected,
generalist core.

@@

Understanding network assembly is particularly relevant to ecological
restoration, which is essentially ``applied succession''
\citep[e.g.,][]{parker1997scale}.  In pollination systems, time has
been shown to affect the structure of networks in restored areas
\citep{forup-2008-742, devoto2012understanding}, suggesting that
interactions change as a community develops. Facilitating network
restoration is especially imperative in areas where species
interactions provide essential ecosystem services, such as crop
pollination in agricultural landscapes. To promote pollinator services
in agriculture, some farmers plant strips of native plants along farm
edges (hedgerows).  By providing habitat, hedgerows augment the
richness, abundance and trait diversity of pollinators in agricultural
landscapes \citep{morandin-2013-829, kremen-2015-602,
  ponisio2015farm}, and promote the persistence and colonization of
floral resource specialists \citep{mgonigle-2015-x}. As the community
assembles, it is important to understand how these new species are
incorporated into the network as well as the consequences of adding
species for interaction patterns and robustness.

@@

In a preferential attachment process, we expect that the most
persistent and high degree species (the species with the most unique
interaction partners) would remain stable in the network core during
assembly \citep{barabasi1999emergence}. Surprisingly, however, we
encountered the opposite pattern. For example, the four most
ubiquitous species in our study landscape --- \textit{Halictus
  ligatus}, \textit{Halictus tripartitus}, \textit{Lasioglossum
  (Dialictus) incompletum}, and \textit{Toxomerus marginatus} --- were
the only species that changed which module they were a member in
across years in all the assembling hedgerows. Because species degree
and persistence were strongly correlated, it is difficult to
disentangle the causal mechanism for why species with those
characteristics are so variable in their network position. Species
that can interact with a relatively high number of partners may be
better able to exploit the limited floral resources in the intensively
managed agriculture landscape, and thus also be the most persistent
\citep[in ant-plant mutualisms, ][]{diaz2010changes}. More persistent
species usually have longer phenologies, so they can visit many
different flowers, resulting in a higher degree \citep{Vazquez2009,
  fort2016abundance}. Either way, our result suggests that adaptable
species can change their network position to utilize the most
advantageous floral resources available, which may depend on both the
other pollinator species that are present and the state of the plant
community \citep{Waser1996, gomez2006ecological,
  macleod2016measuring}. Thus given the opportunity and ability to use
different resources, species will often change their network positions
\citep{macleod2016measuring}.

>>>>

Species in ecological communities are linked through ecological
interactions. As the world continues to lose species at an alarming
rate \citep{dunn2009sixth, barnosky2011has}, anticipating a
community's ability to resist collapse will depend on the strength of
each interaction network and the species within it \citep{Memmott2004,
  Rezende2007, Bascompte2009, Thebault2010}. Furthermore, biodiversity
play a pivotal role in maintaining ecosystems services
\citep{cardinale-2012-59}. Thus, to safeguard ecological function, it
has become increasingly imperative to aid the recovery of lost
interactions and component biodiversity and by facilitating the
assembly of robust interaction networks via ecological restoration
\citep{menz-2010-4}. We know very little, however, about how
ecological networks assemble in general, rendering restoration of
interacting communities quite difficult.

Preferential attachment, the most widely explored mechanism of network
assembly, predicts that species entering a network are more likely to
interact with species that are already well-connected \citep[the
``rich-get-richer'' principle,][]{barabasi1999emergence}.

In
pollination systems --- a particularly ubiquitous mutualism
\citep{ollerton-2011-321, klein-2007-303} --- some studies have found
support for this assembly mechanism. Investigating the day-to-day,
temporal assembly of a plant-pollinator network within a season,
\cite{Olesen2008} found that phenologically new plant and pollinator
species tended to interact with already well-connected species,
potentially because these species are either more abundant or
temporally persistent. Using a space-for-time substitution to study
primary succession, \cite{albrecht2010plant} also found evidence that
assembly along a glacier foreland occurred through preferential
attachment. Specifically, network nestedness (i.e, a core group of
generalists interacts with both specialist and generalist species)
increased as the community aged \citep{albrecht2010plant}. An increase
in nestedness could have occurred via the preferential attachment
process, whereby specialist species attach to the well-connected,
generalist core.

@@

Understanding network assembly is particularly relevant to ecological
restoration, which is essentially ``applied succession''
\citep[e.g.,][]{parker1997scale}.  In pollination systems, time has
been shown to affect the structure of networks in restored areas
\citep{forup-2008-742, devoto2012understanding}, suggesting that
interactions change as a community develops. Facilitating network
restoration is especially imperative in areas where species
interactions provide essential ecosystem services, such as crop
pollination in agricultural landscapes. To promote pollinator services
in agriculture, some farmers plant strips of native plants along farm
edges (hedgerows).  By providing habitat, hedgerows augment the
richness, abundance and trait diversity of pollinators in agricultural
landscapes \citep{morandin-2013-829, kremen-2015-602,
  ponisio2015farm}, and promote the persistence and colonization of
floral resource specialists \citep{mgonigle-2015-x}. As the community
assembles, it is important to understand how these new species are
incorporated into the network as well as the consequences of adding
xspecies for interaction patterns and robustness.

@@

In a preferential attachment process, we expect that the most
persistent and high degree species (the species with the most unique
interaction partners) would remain stable in the network core during
assembly \citep{barabasi1999emergence}. Surprisingly, however, we
encountered the opposite pattern. For example, the four most
ubiquitous species in our study landscape --- \textit{Halictus
  ligatus}, \textit{Halictus tripartitus}, \textit{Lasioglossum
  (Dialictus) incompletum}, and \textit{Toxomerus marginatus} --- were
the only species that changed which module they were a member in
across years in all the assembling hedgerows. Because species degree
and persistence were strongly correlated, it is difficult to
disentangle the causal mechanism for why species with those
characteristics are so variable in their network position. Species
that can interact with a relatively high number of partners may be
better able to exploit the limited floral resources in the intensively
managed agriculture landscape, and thus also be the most persistent
\citep[in ant-plant mutualisms, ][]{diaz2010changes}. More persistent
species usually have longer phenologies, so they can visit many
different flowers, resulting in a higher degree \citep{Vazquez2009,
  fort2016abundance}. Either way, our results suggests that adaptable
species can change their network position to utilize the most
advantageous floral resources available, which may depend on both the
other pollinator species that are present and the state of the plant
community \citep{Waser1996, gomez2006ecological,
  macleod2016measuring}. Thus given the opportunity and ability to use
different resources, species will often change their network positions
\citep{macleod2016measuring}.
